---
title: "simulations"
author: "jasmine cabrera"
format: html
editor: visual
---

## Spherical Simulations

### Effect of k

**Fixed:**

-   Variance: 0.5

-   N: 250

**Test:**

-   k = 2, 3, 4

**Single Run Simulations:**

```{r}
#| label: k = 2
set.seed(590)

# generate data
effect_of_k_data2 <- simulate_mvn(n = 250, variance = 0.5, desired_k = 2)

# plot
effect_of_k_data2 |>
  ggplot(aes(x = X1, y = X2)) +
  geom_point()

# CRAB
k_crab2 <- effect_of_k_data2 |>
  crab_prep() |>
  crab_cols(c("X1", "X2")) |>
  crab_params(min_k = 2, max_k = 5, num_subsamples = 30,
              subsample_prop = 0.85,
              cluster_method = "kmeans") |>
  crab_bake()

k_crab2
write.csv(k_crab2, "k_crab2.csv", row.names = FALSE)
```

```{r}
#| label: k = 3
set.seed(590)

# generate data
effect_of_k_data3 <- simulate_mvn(n = 250, variance = 0.5, desired_k = 3)

# plot
effect_of_k_data3 |>
  ggplot(aes(x = X1, y = X2)) +
  geom_point()

# CRAB
k_crab3 <- effect_of_k_data3 |>
  crab_prep() |>
  crab_cols(c("X1", "X2")) |>
  crab_params(min_k = 2, max_k = 5, num_subsamples = 30,
              subsample_prop = 0.85,
              cluster_method = "kmeans") |>
  crab_bake()

k_crab3
write.csv(k_crab3, "k_crab3.csv", row.names = FALSE)
```

```{r}
#| label: k = 4
set.seed(590)

# generate data
effect_of_k_data4 <- simulate_mvn(n = 250, variance = 0.5, desired_k = 4)

# plot
effect_of_k_data4 |>
  ggplot(aes(x = X1, y = X2)) +
  geom_point()

# CRAB
k_crab4 <- effect_of_k_data4 |>
  crab_prep() |>
  crab_cols(c("X1", "X2")) |>
  crab_params(min_k = 2, max_k = 5, num_subsamples = 30,
              subsample_prop = 0.85,
              cluster_method = "kmeans") |>
  crab_bake()

k_crab4
write.csv(k_crab4, "k_crab4.csv", row.names = FALSE)

```

**Multiple Run Simulations:**

```{r}
#| label: k = 2 (multiple runs)
set.seed(590)

k_crab_mult2 <- crab_prep(data = NULL) |>
  crab_sim_params(n = 250, variance = 0.5, desired_k = 2,
                  min_k = 2, max_k = 5, num_subsamples = 30,
                  subsample_prop = 0.85, num_runs = 25,
                  cluster_method = "kmeans") |>
  repeat_simulations()

k_crab_mult2
write.csv(k_crab_mult2, "k_crab_mult2.csv", row.names = FALSE)
```

```{r}
#| label: k = 3 (multiple runs)
set.seed(590)

k_crab_mult3 <- crab_prep(data = NULL) |>
  crab_sim_params(n = 250, variance = 0.5, desired_k = 3,
                  min_k = 2, max_k = 5, num_subsamples = 30,
                  subsample_prop = 0.85, num_runs = 25,
                  cluster_method = "kmeans") |>
  repeat_simulations()

k_crab_mult3
write.csv(k_crab_mult3, "k_crab_mult3.csv", row.names = FALSE)
```

```{r}
#| label: k = 4 (multiple runs)
set.seed(590)

k_crab_mult4 <- crab_prep(data = NULL) |>
  crab_sim_params(n = 250, variance = 0.5, desired_k = 4,
                  min_k = 2, max_k = 5, num_subsamples = 30,
                  subsample_prop = 0.85, num_runs = 25,
                  cluster_method = "kmeans") |>
  repeat_simulations()

k_crab_mult4
write.csv(k_crab_mult4, "k_crab_mult4.csv", row.names = FALSE)
```

------------------------------------------------------------------------

### Effect of variance

**Fixed:**

-   k: 3

-   N: 250

**Test:**

-   Variance: 0.2, 0.5, 0.8, 1

**Single Run Simulations:**

```{r}
#| label: var = 0.2
set.seed(590)

# generate data
effect_of_var_data2 <- simulate_mvn(n = 250, variance = 0.2, desired_k = 3)

# plot
effect_of_var_data2 |>
  ggplot(aes(x = X1, y = X2)) +
  geom_point()

# CRAB
var_crab2 <- effect_of_var_data2 |>
  crab_prep() |>
  crab_cols(c("X1", "X2")) |>
  crab_params(min_k = 2, max_k = 5, num_subsamples = 30,
              subsample_prop = 0.85,
              cluster_method = "kmeans") |>
  crab_bake()

var_crab2
write.csv(var_crab2, "var_crab2.csv", row.names = FALSE)
```

```{r}
#| label: var = 0.5
set.seed(590)

# generate data
effect_of_var_data5 <- simulate_mvn(n = 250, variance = 0.5, desired_k = 3)

# plot
effect_of_var_data5 |>
  ggplot(aes(x = X1, y = X2)) +
  geom_point()

# CRAB
var_crab5 <- effect_of_var_data5 |>
  crab_prep() |>
  crab_cols(c("X1", "X2")) |>
  crab_params(min_k = 2, max_k = 5, num_subsamples = 30,
              subsample_prop = 0.85,
              cluster_method = "kmeans") |>
  crab_bake()

var_crab5
write.csv(var_crab5, "var_crab5.csv", row.names = FALSE)
```

```{r}
#| label: var = 0.8
set.seed(590)

# generate data
effect_of_var_data8 <- simulate_mvn(n = 250, variance = 0.8, desired_k = 3)

# plot
effect_of_var_data8 |>
  ggplot(aes(x = X1, y = X2)) +
  geom_point()

# CRAB
var_crab8 <- effect_of_var_data8 |>
  crab_prep() |>
  crab_cols(c("X1", "X2")) |>
  crab_params(min_k = 2, max_k = 5, num_subsamples = 30,
              subsample_prop = 0.85,
              cluster_method = "kmeans") |>
  crab_bake()

var_crab8
write.csv(var_crab8, "var_crab8.csv", row.names = FALSE)
```

```{r}
#| label: var = 1
set.seed(590)

# generate data
effect_of_var_data1 <- simulate_mvn(n = 250, variance = 1, desired_k = 3)

# plot
effect_of_var_data1 |>
  ggplot(aes(x = X1, y = X2)) +
  geom_point()

# CRAB
var_crab1 <- effect_of_var_data1 |>
  crab_prep() |>
  crab_cols(c("X1", "X2")) |>
  crab_params(min_k = 2, max_k = 5, num_subsamples = 30,
              subsample_prop = 0.85,
              cluster_method = "kmeans") |>
  crab_bake()

var_crab1
write.csv(var_crab1, "var_crab1.csv", row.names = FALSE)
```

**Multiple Run Simulations:**

```{r}
#| label: var = 0.2, 0.5, 0.8, 1 (multiple runs)
set.seed(590)

var_crab_mult <- crab_prep(data = NULL) |>
  crab_sim_params(n = 250, variance = c(0.2, 0.5, 0.8, 1), desired_k = 3,
                  min_k = 2, max_k = 5, num_subsamples = 30,
                  subsample_prop = 0.85, num_runs = 25,
                  cluster_method = "kmeans") |>
  repeat_simulations()

var_crab_mult
write.csv(var_crab_mult, "var_crab_mult.csv", row.names = FALSE)
```

------------------------------------------------------------------------

### Effect of Sample Size

**Fixed:**

-   Variance: 0.5

-   k: 3

**Test:**

-   N: 100, 250, 400, 750

**Single Run Simulations:**

```{r}
#| label: n = 100
set.seed(590)

# generate data
effect_of_ss_data1 <- simulate_mvn(n = 100, variance = 0.5, desired_k = 3)

# plot
effect_of_ss_data1 |>
  ggplot(aes(x = X1, y = X2)) +
  geom_point()

# CRAB
ss_crab100 <- effect_of_ss_data1 |>
  crab_prep() |>
  crab_cols(c("X1", "X2")) |>
  crab_params(min_k = 2, max_k = 5, num_subsamples = 30,
              subsample_prop = 0.85,
              cluster_method = "kmeans") |>
  crab_bake()

ss_crab100
write.csv(ss_crab100, "ss_crab100.csv", row.names = FALSE)
```

```{r}
#| label: n = 250
set.seed(590)

# generate data
effect_of_ss_data2 <- simulate_mvn(n = 250, variance = 0.5, desired_k = 3)

# plot
effect_of_ss_data2 |>
  ggplot(aes(x = X1, y = X2)) +
  geom_point()

# CRAB
ss_crab250 <- effect_of_ss_data2 |>
  crab_prep() |>
  crab_cols(c("X1", "X2")) |>
  crab_params(min_k = 2, max_k = 5, num_subsamples = 30,
              subsample_prop = 0.85,
              cluster_method = "kmeans") |>
  crab_bake()

ss_crab250
write.csv(ss_crab250, "ss_crab250.csv", row.names = FALSE)
```

```{r}
#| label: n = 400
set.seed(590)

# generate data
effect_of_ss_data3 <- simulate_mvn(n = 400, variance = 0.5, desired_k = 3)

# plot
effect_of_ss_data3 |>
  ggplot(aes(x = X1, y = X2)) +
  geom_point()

# CRAB
ss_crab400 <- effect_of_ss_data3 |>
  crab_prep() |>
  crab_cols(c("X1", "X2")) |>
  crab_params(min_k = 2, max_k = 5, num_subsamples = 30,
              subsample_prop = 0.85,
              cluster_method = "kmeans") |>
  crab_bake()

ss_crab400
write.csv(ss_crab400, "ss_crab400.csv", row.names = FALSE)
```

```{r}
#| label: n = 750
set.seed(590)

# generate data
effect_of_ss_data4 <- simulate_mvn(n = 750, variance = 0.5, desired_k = 3)

# plot
effect_of_ss_data4 |>
  ggplot(aes(x = X1, y = X2)) +
  geom_point()

# CRAB
ss_crab750 <- effect_of_ss_data4 |>
  crab_prep() |>
  crab_cols(c("X1", "X2")) |>
  crab_params(min_k = 2, max_k = 5, num_subsamples = 30,
              subsample_prop = 0.85,
              cluster_method = "kmeans") |>
  crab_bake()

ss_crab750
write.csv(ss_crab750, "ss_crab750.csv", row.names = FALSE)
```

**Multiple Run Simulations:**

```{r}
#| label: n = 100 (multiple runs)
set.seed(590)

ss100_crab_mult <- crab_prep(data = NULL) |>
  crab_sim_params(n = 100, variance = 0.5, desired_k = 3,
                  min_k = 2, max_k = 5, num_subsamples = 30,
                  subsample_prop = 0.85, num_runs = 25,
                  cluster_method = "kmeans") |>
  repeat_simulations()

ss100_crab_mult
write.csv(ss100_crab_mult, "ss100_crab_mult.csv", row.names = FALSE)
```

```{r}
#| label: n = 250 (multiple runs)
set.seed(590)

ss250_crab_mult <- crab_prep(data = NULL) |>
  crab_sim_params(n = 250, variance = 0.5, desired_k = 3,
                  min_k = 2, max_k = 5, num_subsamples = 30,
                  subsample_prop = 0.85, num_runs = 25,
                  cluster_method = "kmeans") |>
  repeat_simulations()

ss250_crab_mult
write.csv(ss250_crab_mult, "ss250_crab_mult.csv", row.names = FALSE)
```

```{r}
#| label: n = 400 (multiple runs) 
set.seed(590)

ss400_crab_mult <- crab_prep(data = NULL) |>
  crab_sim_params(n = 400, variance = 0.5, desired_k = 3,
                  min_k = 2, max_k = 5, num_subsamples = 30,
                  subsample_prop = 0.85, num_runs = 25,
                  cluster_method = "kmeans") |>
  repeat_simulations()

ss400_crab_mult
write.csv(ss400_crab_mult, "ss400_crab_mult.csv", row.names = FALSE)
```

```{r}
#| label: n = 750 (multiple runs) !!!
set.seed(590)

ss750_crab_mult <- crab_prep(data = NULL) |>
  crab_sim_params(n = 750, variance = 0.5, desired_k = 3,
                  min_k = 2, max_k = 5, num_subsamples = 30,
                  subsample_prop = 0.85, num_runs = 25,
                  cluster_method = "kmeans") |>
  repeat_simulations()

ss750_crab_mult
write.csv(ss750_crab_mult, "ss750_crab_mult.csv", row.names = FALSE)
```

------------------------------------------------------------------------

## Spherical Simulations V2.

### Effect of k

**Fixed:**

-   Variance: 0.8

-   N: 400

**Test:**

-   k = 2, 3, 4

**Single Run Simulations:**

```{r}
#| label: k = 2, v2
set.seed(590)

# generate data
effect_of_k_data2_v2 <- simulate_mvn(n = 400, variance = 0.8, desired_k = 2)

# plot
effect_of_k_data2_v2 |>
  ggplot(aes(x = X1, y = X2)) +
  geom_point()

# CRAB
k_crab2_v2 <- effect_of_k_data2_v2 |>
  crab_prep() |>
  crab_cols(c("X1", "X2")) |>
  crab_params(min_k = 2, max_k = 5, num_subsamples = 30,
              subsample_prop = 0.85,
              cluster_method = "kmeans") |>
  crab_bake()

k_crab2_v2 
write.csv(k_crab2_v2, "k_crab2_v2.csv", row.names = FALSE)
```

```{r}
#| label: k = 3, v2
set.seed(590)

# generate data
effect_of_k_data3_v2 <- simulate_mvn(n = 400, variance = 0.8, desired_k = 3)

# plot
effect_of_k_data3_v2 |>
  ggplot(aes(x = X1, y = X2)) +
  geom_point()

# CRAB
k_crab3_v2 <- effect_of_k_data3_v2 |>
  crab_prep() |>
  crab_cols(c("X1", "X2")) |>
  crab_params(min_k = 2, max_k = 5, num_subsamples = 30,
              subsample_prop = 0.85,
              cluster_method = "kmeans") |>
  crab_bake()

k_crab3_v2
write.csv(k_crab3_v2, "k_crab3_v2.csv", row.names = FALSE)
```

```{r}
#| label: k = 4, v2
set.seed(590)

# generate data
effect_of_k_data4_v2 <- simulate_mvn(n = 400, variance = 0.8, desired_k = 4)

# plot
effect_of_k_data4_v2 |>
  ggplot(aes(x = X1, y = X2)) +
  geom_point()

# CRAB
k_crab4_v2 <- effect_of_k_data4_v2 |>
  crab_prep() |>
  crab_cols(c("X1", "X2")) |>
  crab_params(min_k = 2, max_k = 5, num_subsamples = 30,
              subsample_prop = 0.85,
              cluster_method = "kmeans") |>
  crab_bake()

k_crab4_v2
write.csv(k_crab4_v2, "k_crab4_v2.csv", row.names = FALSE)
```

**Multiple Runs:**

```{r}
#| label: k = 2 (multiple runs), v2
set.seed(590)

k_crab_mult2_v2 <- crab_prep(data = NULL) |>
  crab_sim_params(n = 400, variance = 0.8, desired_k = 2,
                  min_k = 2, max_k = 5, num_subsamples = 30,
                  subsample_prop = 0.85, num_runs = 25,
                  cluster_method = "kmeans") |>
  repeat_simulations()

k_crab_mult2_v2
write.csv(k_crab_mult2_v2, "k_crab_mult2_v2.csv", row.names = FALSE)
```

```{r}
#| label: k = 3 (multiple runs), v2
set.seed(590)

k_crab_mult3_v2 <- crab_prep(data = NULL) |>
  crab_sim_params(n = 400, variance = 0.8, desired_k = 3,
                  min_k = 2, max_k = 5, num_subsamples = 30,
                  subsample_prop = 0.85, num_runs = 25,
                  cluster_method = "kmeans") |>
  repeat_simulations()

k_crab_mult3_v2
write.csv(k_crab_mult3_v2, "k_crab_mult3_v2.csv", row.names = FALSE)
```

```{r}
#| label: k = 4 (multiple runs), v2
set.seed(590)

k_crab_mult4_v2 <- crab_prep(data = NULL) |>
  crab_sim_params(n = 400, variance = 0.8, desired_k = 4,
                  min_k = 2, max_k = 5, num_subsamples = 30,
                  subsample_prop = 0.85, num_runs = 25,
                  cluster_method = "kmeans") |>
  repeat_simulations()

k_crab_mult4_v2
write.csv(k_crab_mult4_v2, "k_crab_mult4_v2.csv", row.names = FALSE)
```

### Effect of variance

**Fixed:**

-   k: 3

-   N: 400

**Test:**

-   Variance: 0.2, 0.5, 0.8, 1

**Single Run Simulations:**

```{r}
#| label: var = 0.2, v2
set.seed(590)

# generate data
effect_of_var_data2_v2 <- simulate_mvn(n = 400, variance = 0.2, desired_k = 3)

# plot
effect_of_var_data2_v2 |>
  ggplot(aes(x = X1, y = X2)) +
  geom_point()

# CRAB
var_crab2_v2 <- effect_of_var_data2_v2 |>
  crab_prep() |>
  crab_cols(c("X1", "X2")) |>
  crab_params(min_k = 2, max_k = 5, num_subsamples = 30,
              subsample_prop = 0.85,
              cluster_method = "kmeans") |>
  crab_bake()

var_crab2_v2
write.csv(var_crab2_v2, "var_crab2_v2.csv", row.names = FALSE)
```

```{r}
#| label: var = 0.5, v2 
set.seed(590)

# generate data
effect_of_var_data5_v2 <- simulate_mvn(n = 400, variance = 0.5, desired_k = 3)

# plot
effect_of_var_data5_v2 |>
  ggplot(aes(x = X1, y = X2)) +
  geom_point()

# CRAB
var_crab5_v2 <- effect_of_var_data5_v2 |>
  crab_prep() |>
  crab_cols(c("X1", "X2")) |>
  crab_params(min_k = 2, max_k = 5, num_subsamples = 30,
              subsample_prop = 0.85,
              cluster_method = "kmeans") |>
  crab_bake()

var_crab5_v2
write.csv(var_crab5_v2, "var_crab5_v2.csv", row.names = FALSE)
```

```{r}
#| label: var = 0.8, v2 
set.seed(590)

# generate data
effect_of_var_data8_v2 <- simulate_mvn(n = 400, variance = 0.8, desired_k = 3)

# plot
effect_of_var_data8_v2 |>
  ggplot(aes(x = X1, y = X2)) +
  geom_point()

# CRAB
var_crab8_v2 <- effect_of_var_data8_v2 |>
  crab_prep() |>
  crab_cols(c("X1", "X2")) |>
  crab_params(min_k = 2, max_k = 5, num_subsamples = 30,
              subsample_prop = 0.85,
              cluster_method = "kmeans") |>
  crab_bake()

var_crab8_v2
write.csv(var_crab8_v2, "var_crab8_v2.csv", row.names = FALSE)
```

```{r}
#| label: var = 1, v2 
set.seed(590)

# generate data
effect_of_var_data1_v2 <- simulate_mvn(n = 400, variance = 1, desired_k = 3)

# plot
effect_of_var_data1_v2 |>
  ggplot(aes(x = X1, y = X2)) +
  geom_point()

# CRAB
var_crab1_v2 <- effect_of_var_data1_v2 |>
  crab_prep() |>
  crab_cols(c("X1", "X2")) |>
  crab_params(min_k = 2, max_k = 5, num_subsamples = 30,
              subsample_prop = 0.85,
              cluster_method = "kmeans") |>
  crab_bake()

var_crab1_v2
write.csv(var_crab1_v2, "var_crab1_v2.csv", row.names = FALSE)
```

**Multiple Runs:**

```{r}
#| label: var = 0.2, 0.5, 0.8, 1 (multiple runs) v2 !!!
set.seed(590)

var_crab_mult_v2 <- crab_prep(data = NULL) |>
  crab_sim_params(n = 400, variance = c(0.2, 0.5, 0.8, 1), desired_k = 3,
                  min_k = 2, max_k = 5, num_subsamples = 30,
                  subsample_prop = 0.85, num_runs = 25,
                  cluster_method = "kmeans") |>
  repeat_simulations()

var_crab_mult_v2
write.csv(var_crab_mult_v2, "var_crab_mult_v2.csv", row.names = FALSE)
```

### Effect of Sample Size

**Fixed:**

-   Variance: 0.8

-   k: 3

**Test:**

-   N: 100, 250, 400, 750

**Single Run Simulations:**

```{r}
#| label: n = 100, v2 
set.seed(590)

# generate data
effect_of_ss_data1_v2 <- simulate_mvn(n = 100, variance = 0.8, desired_k = 3)

# plot
effect_of_ss_data1_v2 |>
  ggplot(aes(x = X1, y = X2)) +
  geom_point()

# CRAB
ss_crab100_v2 <- effect_of_ss_data1_v2 |>
  crab_prep() |>
  crab_cols(c("X1", "X2")) |>
  crab_params(min_k = 2, max_k = 5, num_subsamples = 30,
              subsample_prop = 0.85,
              cluster_method = "kmeans") |>
  crab_bake()

ss_crab100_v2
write.csv(ss_crab100_v2, "ss_crab100_v2.csv", row.names = FALSE)
```

```{r}
#| label: n = 250, v2 
set.seed(590)

# generate data
effect_of_ss_data2_v2 <- simulate_mvn(n = 100, variance = 0.8, desired_k = 3)

# plot
effect_of_ss_data2_v2 |>
  ggplot(aes(x = X1, y = X2)) +
  geom_point()

# CRAB
ss_crab250_v2 <- effect_of_ss_data2_v2 |>
  crab_prep() |>
  crab_cols(c("X1", "X2")) |>
  crab_params(min_k = 2, max_k = 5, num_subsamples = 30,
              subsample_prop = 0.85,
              cluster_method = "kmeans") |>
  crab_bake()

ss_crab250_v2
write.csv(ss_crab250_v2, "ss_crab250_v2.csv", row.names = FALSE)
```

```{r}
#| label: n = 400, v2 
set.seed(590)

# generate data
effect_of_ss_data3_v2 <- simulate_mvn(n = 400, variance = 0.8, desired_k = 3)

# plot
effect_of_ss_data3_v2 |>
  ggplot(aes(x = X1, y = X2)) +
  geom_point()

# CRAB
ss_crab400_v2 <- effect_of_ss_data3_v2 |>
  crab_prep() |>
  crab_cols(c("X1", "X2")) |>
  crab_params(min_k = 2, max_k = 5, num_subsamples = 30,
              subsample_prop = 0.85,
              cluster_method = "kmeans") |>
  crab_bake()

ss_crab400_v2
write.csv(ss_crab400_v2, "ss_crab400_v2.csv", row.names = FALSE)
```

```{r}
#| label: n = 750, v2 
set.seed(590)

# generate data
effect_of_ss_data4_v2 <- simulate_mvn(n = 750, variance = 0.8, desired_k = 3)

# plot
effect_of_ss_data4_v2 |>
  ggplot(aes(x = X1, y = X2)) +
  geom_point()

# CRAB
ss_crab750_v2 <- effect_of_ss_data4_v2 |>
  crab_prep() |>
  crab_cols(c("X1", "X2")) |>
  crab_params(min_k = 2, max_k = 5, num_subsamples = 30,
              subsample_prop = 0.85,
              cluster_method = "kmeans") |>
  crab_bake()

ss_crab750_v2
write.csv(ss_crab750_v2, "ss_crab750_v2.csv", row.names = FALSE)
```

**Multiple Runs:**

```{r}
#| label: n = 100 (multiple runs) v2 !!!
set.seed(590)

ss100_crab_mult_v2 <- crab_prep(data = NULL) |>
  crab_sim_params(n = 100, variance = 0.8, desired_k = 3,
                  min_k = 2, max_k = 5, num_subsamples = 30,
                  subsample_prop = 0.85, num_runs = 25,
                  cluster_method = "kmeans") |>
  repeat_simulations()

ss100_crab_mult_v2
write.csv(ss100_crab_mult_v2, "ss100_crab_mult_v2.csv", row.names = FALSE)
```

```{r}
#| label: n = 250 (multiple runs) v2 !!!
set.seed(590)

ss250_crab_mult_v2 <- crab_prep(data = NULL) |>
  crab_sim_params(n = 250, variance = 0.8, desired_k = 3,
                  min_k = 2, max_k = 5, num_subsamples = 30,
                  subsample_prop = 0.85, num_runs = 25,
                  cluster_method = "kmeans") |>
  repeat_simulations()

ss250_crab_mult_v2
write.csv(ss250_crab_mult_v2, "ss250_crab_mult_v2.csv", row.names = FALSE)
```

```{r}
#| label: n = 400 (multiple runs) v2 !!!
set.seed(590)

ss400_crab_mult_v2 <- crab_prep(data = NULL) |>
  crab_sim_params(n = 400, variance = 0.8, desired_k = 3,
                  min_k = 2, max_k = 5, num_subsamples = 30,
                  subsample_prop = 0.85, num_runs = 25,
                  cluster_method = "kmeans") |>
  repeat_simulations()

ss400_crab_mult_v2
write.csv(ss400_crab_mult_v2, "ss400_crab_mult_v2.csv", row.names = FALSE)
```

```{r}
#| label: n = 750 (multiple runs) v2 !!!
set.seed(590)

ss750_crab_mult_v2 <- crab_prep(data = NULL) |>
  crab_sim_params(n = 750, variance = 0.8, desired_k = 3,
                  min_k = 2, max_k = 5, num_subsamples = 30,
                  subsample_prop = 0.85, num_runs = 25,
                  cluster_method = "kmeans") |>
  repeat_simulations()

ss750_crab_mult_v2
write.csv(ss750_crab_mult_v2, "ss750_crab_mult_v2.csv", row.names = FALSE)
```
